Omics-based Single Step Trait Prediction

### 2017-03-15 reports/Paper.Rmd
Init LaTeX paper

@@

>>>>

---
title: Omics-based Single Step Trait Prediction
author:
  - name: Matthias Westhues
    email: matthias.westhues@uni-hohenheim.de
    affiliation: University of Hohenheim
  - name: Claas Heuer
    email: cheuer@tierzucht.uni-kiel.de
    affiliation: University of Kiel
  - name: Georg Thaller
    email: thaller@tierzucht.uni-kiel.de
    affiliation: University of Kiel
  - name: Rohan Fernando
    email: rohan@iastate.edu
    affiliation: Iowa State University
  - name: Albrecht E. Melchinger
    email: melchinger@uni-hohenheim.de
    affiliation: University of Hohenheim
    footnote: Corresponding Author
address:
  - code: University of Hohenheim
    address: Institute of Plant Breeding, Seed Science and Population Genetics, Fruwirthstr. 21, 70599 Stuttgart, Germany
  - code: University of Kiel
    address: Institut of Animal Breeding and Husbandry, Hermann-Rodewald-Straße 6, 24118 Kiel, Germany
  - code: Iowa State University
    address: Department of Animal Science, 239 Kildee Hall, 50011 Ames, Iowa, U.S.A.
date: "`r Sys.Date()`"
knit: "bookdown::render_book"
output:
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
bibliography: ["~/Dropbox/Paper/library.bib"]
abstract: |
  $\dots$
---

<!--chapter:end:index.Rmd-->

# Introduction
$\dots$

Our objectives were threefold: (1) Examine whether the single step prediction
framework can be transfered to hybrids, (2) explore the utility of single step 
predition with a quantitative predictor and (3) evaluate the impact of the
particular genetic space covered by the incomplete predictor on predictive
ability.

<!--chapter:end:introduction.Rmd-->

@@

<!--chapter:end:methods.Rmd-->

# Results

![Bullshit]("./tabs_figs/core_fraction_predictive_ability_trend.pdf")

<!--
\begin{figure}[H]
\centering
\includegraphics{./tabs_figs/core_fraction_predictive_ability_trend.pdf}
\caption{
Influence of core set composition on predictive abilities.
Predictive abilities are based on single step predition with genomic data as the 
complete predictor and transcriptomic data as the incomplete predictor.
Results are shown for six agronomic traits and nine core sets of the maize 
diversity panel.
}
\label{fig:CoreSetInfluence}
\end{figure}
-->

<!--
% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 15 10:35:35 2017
# Script: ./analysis/maizego_plot_predictive_abilities.R
-->
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for the set of 211 tropical/subtropical lines from the maize diversity panel.} 
\begin{tabular}{rllllll}
  \toprule
 & 100grainweight & cobweight & Eardiameter & Kernelwidth & Plantheight & Silkingtime \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: no}}\\
snp-mrna & 0.44 (0.0748) & 0.33 (0.1727) & 0.4 (0.0543) & 0.34 (0.0425) & 0.4 (0.0707) & 0.53 (0.0285) \\ 
  snp-none & 0.43 (0.0733) & 0.37 (0.1734) & 0.39 (0.0535) & 0.34 (0.0455) & 0.45 (0.0755) & 0.53 (0.0297) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: yes}}\\
mrna-none & 0.4 (0.0747) & 0.15 (0.1568) & 0.37 (0.0509) & 0.36 (0.0423) & 0.32 (0.0692) & 0.49 (0.0279) \\ 
  snp-none1 & 0.36 (0.0773) & 0.21 (0.1678) & 0.3 (0.0527) & 0.34 (0.0472) & 0.41 (0.078) & 0.45 (0.0302) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

<!--
% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 15 11:11:37 2017
# Script: ./analysis/uhoh_plot_predictive_abilities.R
-->
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for the set of maize hybrids} 
\begin{tabular}{rllllll}
  \toprule
 & DMY & DMC & FAT & PRO & STA & SUG \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
ped-none & 0.54 (0.0493) & 0.48 (0.0521) & 0.21 (0.0365) & 0.6 (0.0187) & 0.35 (0.0427) & 0.42 (0.117) \\ 
  snp-none & 0.74 (0.0517) & 0.63 (0.0521) & 0.43 (0.0356) & 0.65 (0.0223) & 0.46 (0.0458) & 0.47 (0.1261) \\ 
  ped-snp & 0.71 (0.054) & 0.57 (0.0545) & 0.35 (0.0375) & 0.62 (0.0235) & 0.39 (0.0478) & 0.42 (0.1298) \\ 
  ped-mrna & 0.73 (0.056) & 0.53 (0.0594) & 0.35 (0.0398) & 0.61 (0.0254) & 0.31 (0.0504) & 0.37 (0.1396) \\ 
  snp-mrna & 0.75 (0.0533) & 0.61 (0.0553) & 0.43 (0.0374) & 0.65 (0.0239) & 0.44 (0.048) & 0.44 (0.1342) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
mrna-none & 0.75 (0.0552) & 0.34 (0.0619) & 0.4 (0.0412) & 0.47 (0.0293) & 0.16 (0.0496) & 0.27 (0.1447) \\ 
  ped-none1 & 0.46 (0.0469) & 0.53 (0.05) & 0.23 (0.0368) & 0.46 (0.0234) & 0.38 (0.0391) & 0.34 (0.1316) \\ 
  snp-none1 & 0.67 (0.0534) & 0.47 (0.0552) & 0.43 (0.0384) & 0.48 (0.027) & 0.36 (0.0457) & 0.35 (0.132) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

<!--
% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 15 11:36:08 2017
# Script: ./analysis/maizego_core_fraction_plot_predictive_abilities.R
-->
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for different core sets from the tropical/subtropical material of the maize diversity panel.} 
\begin{tabular}{rllllll}
  \toprule
 & 100grainweight & cobweight & Eardiameter & Kernelwidth & Plantheight & Silkingtime \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
snp-mrna & 0.44 (0.0748) & 0.33 (0.1727) & 0.4 (0.0543) & 0.34 (0.0425) & 0.4 (0.0707) & 0.53 (0.0285) \\ 
  snp-none & 0.43 (0.0733) & 0.37 (0.1734) & 0.39 (0.0535) & 0.34 (0.0455) & 0.45 (0.0755) & 0.53 (0.0297) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
mrna-none\_1.0 & 0.4 (0.0747) & 0.15 (0.1568) & 0.37 (0.0509) & 0.36 (0.0423) & 0.32 (0.0692) & 0.49 (0.0279) \\ 
  snp-mrna\_0.3 & 0.36 (0.0711) & 0.2 (0.1566) & 0.28 (0.0503) & 0.37 (0.044) & 0.42 (0.0736) & 0.5 (0.028) \\ 
  snp-mrna\_0.4 & 0.39 (0.0697) & 0.2 (0.1558) & 0.33 (0.0486) & 0.35 (0.0428) & 0.38 (0.0727) & 0.52 (0.028) \\ 
  snp-mrna\_0.5 & 0.41 (0.0671) & 0.16 (0.1549) & 0.31 (0.0486) & 0.4 (0.0414) & 0.44 (0.0748) & 0.49 (0.0278) \\ 
  snp-mrna\_0.6 & 0.4 (0.0739) & 0.13 (0.1563) & 0.27 (0.0497) & 0.37 (0.0417) & 0.42 (0.075) & 0.55 (0.0272) \\ 
  snp-mrna\_0.7 & 0.37 (0.0734) & 0.1 (0.1555) & 0.31 (0.0508) & 0.37 (0.0422) & 0.33 (0.0755) & 0.52 (0.028) \\ 
  snp-mrna\_0.8 & 0.4 (0.0774) & 0.21 (0.1581) & 0.36 (0.0515) & 0.41 (0.0458) & 0.29 (0.0737) & 0.49 (0.0288) \\ 
  snp-mrna\_0.9 & 0.39 (0.0792) & 0.21 (0.1692) & 0.38 (0.0561) & 0.41 (0.0459) & 0.29 (0.075) & 0.49 (0.0311) \\ 
  snp-none\_1.0 & 0.36 (0.0773) & 0.21 (0.1678) & 0.3 (0.0527) & 0.34 (0.0472) & 0.41 (0.078) & 0.45 (0.0302) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

<!--chapter:end:results.Rmd-->

# Discussion

<!--chapter:end:discussion.Rmd-->

# References

<!--chapter:end:references.Rmd-->
